Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
fixed genus 1 base cases to include canonical divisor as half canonical divisor

\begin{enumerate}
	\item $\halfcan' = 0$
	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3.$
\end{enumerate}

@@

\begin{example}
\label{eg:base-1-33}
Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. In this example, we show
$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$$
and that $(\sx',\{3,3\})$ is admissible.

@@

@@

\todo{cite genus 1 final theorem here, to explain what these cases are exceptional to}
\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$(1;-; 0)$ & $\{2\}$ & $\emptyset$ \\	\hline

	$(1; 3; 0)$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline

	$(1; 5; 0)$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline

@@

We now elaborate on the computation of the results in 
Table ~\ref{table:g-1-exceptional}. In the following example we will explain the case $\sigma = (1;5;0)$ as the other cases are even easier.

@@

\begin{example}
\label{eg:exception-1-5}
Let $L = P - Q + \frac{2}{5}R_1$ be a half canonical divisor on a stacky curve $\sx$. Let $u \in (R_L)_1$ be any nonzero element. We obtain $\di u|_R = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (R_L)_1 = 1$ let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_R = - R,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_R = -R$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $R$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$. It is analogous to Example ~\ref{ex:base-377}, and is omittied.
\end{example}

>>>>

\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$0$ & $\{1\}$ & $\emptyset$ \\	\hline

	$P-Q + \frac{2}{5}R_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline

	$\frac{3}{7}R_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline

	$P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ \\	\hline

%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10,\ldots, e+2, e+3, e+5,e+7,\ldots, 2e-4\}$ \\	\hline
\end{longtable}
\begin{enumerate}
	\item $\halfcan' = 0$
	\item $\halfcan' = P - Q + \frac{2}{5}R_1.$
	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2.$
	\item $\halfcan' = \frac{3}{7}R_1.$
\end{enumerate}
\todo{Is it ok that two genus 1 base cases are also exceptional, in terms of their relation degree?}

@@

\begin{example}
\label{eg:base-1-33}
Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. In this example, we show
$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(x_3 y_3- \alpha uy_4,y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
and that $(\sx',\{3,3\})$ is admissible.

@@

\begin{example}
\label{eg:exception-1-5}
Let $L' = \frac{2}{5}R_1$ be a half canonical divisor on a stacky curve $\sx$. Let $u \in (R_L)_1$ be any nonzero element. We obtain $\di u|_{R_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (R_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_{R_1} = - R_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{R_1} = -R_1$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $R_1$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$. It is analogous to Example ~\ref{ex:base-377}, and is omittied.

Note that $L'$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.

Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Theorem ~\ref{thm:ram_order_ind}, this relation in degree 12 caries over, and so the case $L' = P - Q + \frac{3}{7}R_1$ is not exceptional because $12 < 2 \cdot 7$.
\end{example}

\iffalse
The base case of $L' = \frac{3}{7}R_1$ has $R_L \cong k[u,y_5,y_7]/(y_5)^3 - uy_7^2.$ 
\fi

The base case of $L' = \frac{3}{7}R_1$ can be similarly computed. Note this is yet another exceptional case.

@@

\todo{cite genus 1 final theorem here, to explain what these cases are exceptional to}
\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$P-Q$ & $\{2\}$ & $\emptyset$ \\	\hline

	$P-Q + \frac{1}{3}R_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline

	$P-Q + \frac{2}{5}R_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline

	$\frac{1}{3}R_1$ & $\{1,6,9\}$ & $\{18\}$ \\	\hline

	$\frac{2}{5}R_1$ & $\{1,5,8\}$ & $\{16\}$ \\	\hline

	$\frac{3}{7}R_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline

@@

We now elaborate on the computation of the results in 
Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
$L' = P-Q + \frac{1}{5}R_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.

@@
